Quantifying and controlling biases in dark matter halo concentration estimates

### 2016-08-11 paper/ms.tex

The thin continous lines on the same panel shows a fit to the data
with the following functional form 
\begin{equation}
f_{\rm off} = \frac{A}{(1+\log_{10}N_s)^{B}}.
\label{eq:f_off_fit}
\end{equation} 
for the dataset shown in the panel we find $A=2842\pm 1900$,
$B=7.96\pm 0.54$ for the density method; $A=239\pm 131$,
$B=6.23\pm 0.43$ for the velocity method; $A=-3.66\pm 5.22$,
$B=4.65\pm 1.12$ for the integrated mass method.
The uncertainties are estimated from the covariance  matrix resulting
from the non-linear optimization procedure. The lines on Figure
\ref{fig:downsampling} are plotted using these best values.

>>>>

The thin continous lines on the same panel shows a fit to the data
with the following functional form 
\begin{equation}
f_{\rm off} = \frac{A}{(1+\log_{10}N_s)^{B}}.
\label{eq:f_off_fit}
\end{equation} 
for the dataset shown in the panel we find $A=2842\pm 1900$,
$B=7.96\pm 0.54$ for the density method; $A=239\pm 131$,
$B=6.23\pm 0.43$ for the velocity method; $A=-0.46\pm 3.49$,
$B=0.79\pm 1.31$ for the integrated mass method.
The uncertainties are estimated from the covariance  matrix resulting
from the non-linear optimization procedure. The lines on Figure
\ref{fig:downsampling} are plotted using these best values.
